Evaluating computational methods for modeling off-normal operation of gas centrifuge cascades

### 2020-10-29 theory.tex
Last inclusion of Raetz information.

\begin{eqnarray}
    \delta U(L,F,\theta,Z_{p}) &= &\frac{1}{2}
            F\theta(1 - \theta)
            \left(\frac{\Delta M}{2 RT}v_{a}^{2}\right)^{2}
            \left(\frac{r_{2}}{a}\right)^{4}
            \left[1 - \left(\frac{r_{1}}{r_{2}}\right)^{2}\right]^{2}
            \label{eq_raetz}\\
        &&
            \left[
                \left(\frac{1+L/F}{\theta}\right)
                (1- exp[ - A_{P}(L,F,\theta)Z_{p}])  \nonumber  \right. \\
        &&~~ + \left.\left(\frac{L/F}{1 - \theta}\right)
                (1 - exp[ -A_{W}(L,F,\theta)(Z - Z_{p}])\right]^{2}, \nonumber
                \\
    \textrm{with~ ~ ~ ~ ~}
        A_{P} &= &\frac{2\pi D\rho }{ ln(r_{2}/r_{1}) }
                 \frac{ 1 }{ F }
                 \frac{ 1-\theta }{(1+L/F)(1-\theta+L/F) }\\
        A_{W} &= &\frac{2\pi D\rho }{ ln(r_{2}/r_{1}) }
                 \frac{ 1 }{ F }
                 \frac{ 1-\theta }{ (L/F)(1-\theta+L/F) }
\end{eqnarray}

@@

Here the gas constants are mass, $M$, temperature $T$, universal gas constant, $R$,
and the pressure ratio, $x$ (typically $1000:1$).
This relationship is valid when $v_a > 380 \frac{\mathrm{m}}{\mathrm{s}}$.
Otherwise, the relationship can be approximated ${\frac{r_1}{r_2} \approx 0.534 \mid v_a \leq 380} \frac{\mathrm{m}}{\mathrm{s}}$.

>>>>

\begin{eqnarray}
    \label{eq:raetz}
    \delta U(L,F,\theta,Z_{p}) &= &\frac{1}{2}
            F\theta(1 - \theta)
            \left(\frac{\Delta M}{2 RT}v_{a}^{2}\right)^{2}
            \left(\frac{r_{2}}{a}\right)^{4}
            \left[1 - \left(\frac{r_{1}}{r_{2}}\right)^{2}\right]^{2}
            \label{eq_raetz}\\
        &&
            \left[
                \left(\frac{1+L/F}{\theta}\right)
                (1- exp[ - A_{P}(L,F,\theta)Z_{p}])  \nonumber  \right. \\
        &&~~ + \left.\left(\frac{L/F}{1 - \theta}\right)
                (1 - exp[ -A_{W}(L,F,\theta)(Z - Z_{p}])\right]^{2}, \nonumber
                \\
    \textrm{with~ ~ ~ ~ ~}
        A_{P} &= &\frac{2\pi D\rho }{ ln(r_{2}/r_{1}) }
                 \frac{ 1 }{ F }
                 \frac{ 1-\theta }{(1+L/F)(1-\theta+L/F) }\\
        A_{W} &= &\frac{2\pi D\rho }{ ln(r_{2}/r_{1}) }
                 \frac{ 1 }{ F }
                 \frac{ 1-\theta }{ (L/F)(1-\theta+L/F) }
\end{eqnarray}

@@

Here the gas constants are molar mass, $M$, temperature $T$, universal gas constant, $R$,
and the pressure ratio, $x$ (typically $1000:1$).
This relationship is valid when $v_a > 380 \frac{\mathrm{m}}{\mathrm{s}}$.
Otherwise, the relationship can be approximated ${\frac{r_1}{r_2} \approx 0.534 \mid v_a \leq 380} \frac{\mathrm{m}}{\mathrm{s}}$.
In order to decompose the ratio into each individual radius, knowledge on one
of them is required. Glaser \cite{glaser.2008} states that $r_2$ typically ranges
from 96% to 99% the value of the inner centrifuge wall radius $a$. The exact
behavior of $r_2$ between these two values in operational conditions is unknown,
but a linear approximation can be made. It is assumed that $r_2$ is always at
the midpoint of these two extremes (i.e. $r_2 = 0.975 a$). Then, $r_1$ can be
found by simply multiplying this value by the ratio.

With this, all parameters of the separative power equation \ref{eq:raetz} are
defined and a value can be calculated. $\delta U$ has units similar to the feed
flow, that of $[mg/s]$.
